First look at Spacetime

### 2019-10-28 Output/error_reduction_analysis.tex
final change

Denote the $2 \times 2$ block-matrix with $M$. We use MINRES with initial guess $x_0$
equal to the right-hand side $b$ of the system, and continue until the relative residual norm is `small':
\[
  \frac{\|Mx_k - b\|_2}{\|b\|_2} \leq 10^{-5}.
\]
This gives us a discrete solution $(\mu_\delta, u_\delta)$ for which we can measure
\[
  E(t) := t \mapsto \|\gamma_t(u_\delta - u)\|_{L_2(\Omega)}
\]
by computing
\[
  E(t)^2 = \inp{u(t)}{u(t)}_{L_2(\Omega)} + \inp{u_\delta(t)}{u_\delta(t)}_{L_2(\Omega)} - 2 \inp{u(t)}{u_\delta(t)}_{L_2(\Omega)}
\]
where we have the first term analytically, the second number can be computed by
an applicator of the space-time mass matrix, and the final term is approximated
using quadrature of sufficient degree. We will use this as a proxy for the error
$\|u - u_\delta\|_X$, which is difficult to measure.

>>>>

Denote the $2 \times 2$ block-matrix with $M$. We use MINRES with initial guess $x_0$
equal to the right-hand side $b$ of the system, and continue until the relative residual norm is `small':
\[
  \frac{\|Mx_k - b\|_2}{\|b\|_2} \leq 10^{-5}.
\]
This gives us a discrete solution $(\mu_\delta, u_\delta)$ for which we can measure
\[
  E(t) := t \mapsto \|\gamma_t(u_\delta - u)\|_{L_2(\Omega)}
\]
by computing
\[
  E(t)^2 = \inp{u(t)}{u(t)}_{L_2(\Omega)} + \inp{u_\delta(t)}{u_\delta(t)}_{L_2(\Omega)} - 2 \inp{u(t)}{u_\delta(t)}_{L_2(\Omega)}
\]
where we have the first term analytically, the second number can be computed by
an applicator of the space-time mass matrix, and the final term is found
using quadrature of sufficient degree. We will use this as a proxy for the error
$\|u - u_\delta\|_X$, which is difficult to measure.
